---
title: "p8105_hw6_mnw2132"
author: "Mary Williams"
date: "2024-11-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(broom)
```

#Question 1

## Loading the data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
# Compute r^2 and log(beta0 * beta1)
compute_quantities <- function(data) {
  model <- lm(tmax ~ tmin, data = data)
  r_squared <- glance(model)$r.squared
  coefs <- tidy(model)
  log_beta_product <- log(coefs$estimate[1] * coefs$estimate[2])
  return(tibble(r_squared = r_squared, log_beta_product = log_beta_product))
}

# 5000 bootstrap samples
set.seed(123)  
bootstrap_results <- map_dfr(1:5000, ~ {
  resampled_data <- weather_df %>% sample_frac(replace = TRUE)
  compute_quantities(resampled_data)
})
```

## Plot distribution
```{r}
summary(bootstrap_results)
# Pivot longer
bootstrap_results %>%
  pivot_longer(cols = everything(), names_to = "quantity", values_to = "value") %>%
  
  #Plot the distribution
  ggplot(aes(x = value)) +
  geom_density(fill = "lightpink", alpha = 0.7) +
  facet_wrap(~quantity, scales = "free") +
  labs(title = "5000 Bootstrap of r squared and log(beta0 * beta1)",
       x = "Value", y = "Density of value")
```
geom_point did not show the data clearly, so instead I used geom_density to show the density of the points. According to the density graph, the data shows a bell curve. The log(beta0 * beta1) peaks around 16 with a mean density of about 2.15, while r squared peaked around 46, with a density mean of about 0.91. 


## Confidence Intervals and quantiles
```{r}
bootstrap_results %>%
  group_by() %>%
  summarise(
    r_lower = quantile(r_squared, 0.025),
    r_upper = quantile(r_squared, 0.975),
    log_lower = quantile(log_beta_product, 0.025),
    log_upper = quantile(log_beta_product, 0.975)
  )
```
The 95% CIs and quantiles for the r squared was (0.895, 0.927) and for the log is (1.96, 2.06). 

# Question 2 
```{r}
#Load data
homicide_df <- read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")

# Tidy data
homicide_df_tidy <- homicide_df %>%
    mutate(
    city_state = paste (city,state, sep = ","),
    resolved = ifelse(disposition == "Closed by arrest", 1, 0),
    victim_age = as.numeric(victim_age),
    victim_race = str_to_lower(victim_race)
  ) %>%
    filter(!(city %in% c("Dallas", "Phoenic","Kansas City", "Tulsa")),
    victim_race %in% c("white","black"),
    !is.na(victim_age)
) 
```

## Baltimore
```{r}
# Filter for Baltimore, MD
baltimore <- homicide_df_tidy %>% 
  filter(city == "Baltimore")

# Logistic regression got males vs females
baltimore_glm <- glm(resolved ~ victim_age + victim_sex + victim_race, 
                     data = baltimore, 
                     family = "binomial")

baltimore_results <- broom::tidy(baltimore_glm, exp = TRUE)

male_vs_female <- baltimore_results %>% filter(term == "victim_sexMale")
male_vs_female
```

## All cities
```{r}
# Group by city and fit logistic regression models for each city
city_results <- homicide_df_tidy %>%
  group_by(city_state) %>%
  nest() %>%
  mutate(
    glm_model = map(data, ~ glm(resolved ~ victim_age + victim_sex + victim_race, 
                                data = ., 
                                family = "binomial")),
    results = map(glm_model, ~ broom::tidy(., conf.int = TRUE, exp = TRUE))
  ) %>%
  unnest(results) %>%
  filter(term == "victim_sexMale") %>%
  select(city_state, estimate, conf.low, conf.high)
```

## Visualize OR
```{r}
# Reorder cities by odds ratio for visualization
city_results <- city_results %>%
  mutate(city_state = fct_reorder(city_state, estimate))

# Plot ORs and confidence intervals
ggplot(city_results, aes(x = city_state, y = estimate, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange(color = "pink") +
  labs(
    title = "Adjusted ORs for Solving Homicides by City by Gender",
    x = "City",
    y = "Adjusted OR (Male vs Female)",
  ) +
  theme(axis.text.x = element_text(angle = 90))
```

# Question 3
```{r}
library(modelr)
library(broom)
```

```{r}
# Load the data 
birthweight_df <- read.csv("./birthweight.csv")
summary(birthweight_df)

# Convert factors
birthweight_factor <- birthweight_df %>%
  mutate(
    babysex = factor(babysex, levels = c(1, 2), labels = c("Male", "Female")),
    frace = factor(frace, levels = c(1, 2, 3, 4, 8, 9), labels = c("White", "Black", "Asian", "Puerto Rican", "Other", "Unknown")),
    mrace = factor(mrace, levels = c(1, 2, 3, 4, 8), labels = c("White", "Black", "Asian", "Puerto Rican", "Other")),
    malform = factor(malform, levels = c(0, 1), labels = c("No", "Yes"))
  )

summary(birthweight_factor)
```

```{r}
# Regression model of baby's weight has any relation to mother's weight, health, and demographic factors
bby_weight = lm(bwt ~ delwt + mheight + momage + mrace + ppbmi + ppwt + smoken + wtgain, data = birthweight_factor)

broom::tidy(bby_weight)
```

```{r}
# Plot residuals vs fitted values
birthweight_factor  %>% 
  add_predictions(bby_weight) %>%  
  add_residuals(bby_weight) %>% 
  ggplot(aes(x = pred, y= resid)) + 
  geom_point(color = "blue") + 
  geom_point(aes(y = pred), color = "pink")+
  labs(title = "Residuals vs Fitted", x = "Fitted Values", y = "Residuals") +
  theme_minimal()
```
